### 2022-04-30 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@513ca395296bee28e4275a7dae38173958673138 🚀

Despite the difference in evolutionary distinctiveness globally, there
are reasons to expect that the phylogeography of bats and
betacoronaviruses should show some degree of congruence. High density of
hosts sharing the same virus (albeit possibly different strains) can
drive or result from evolution of the bat antiviral immune system,
resulting in spatially distinct immunological responses, as evidenced in
several bat species (Banerjee et al. 2020). Immune characteristics that
allow bats to be better adapted to infection by emerging viruses
(Gorbunova et al., 2020; Irving et al., 2021) may be related to a wide
variety of diets (Jones et al., 2022; Moreno Santillán et al., 2021;
Banerjee et al., 2020; Schneeberger et al., 2013; Muylaert et al.,
2021), themselves likely to be driven by spatial effect, especially at
the local scale -- bats, indeed, occupy a variety of environments.

\begin{figure}
\hypertarget{fig:biogeo}{%
\centering
\includegraphics{figures/combined_biogeo.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:biogeo}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:trivariate}
}
\end{figure}

>>>>

Despite the difference in evolutionary distinctiveness globally, there
are reasons to expect that the phylogeography of bats and
betacoronaviruses should show some degree of congruence. High density of
hosts sharing the same virus (albeit possibly different strains) can
drive or result from evolution of the bat antiviral immune system,
resulting in spatially distinct immunological responses, as evidenced in
several bat species (Banerjee et al. 2020). Immune characteristics that
allow bats to be better adapted to infection by emerging viruses
(Gorbunova et al., 2020; Irving et al., 2021), in addition to being
hardcoded in their genome (\textbf{Jebb et al.~six\ldots{}}), may be
related to a wide variety of diets (Jones et al., 2022; Moreno Santillán
et al., 2021; Banerjee et al., 2020; Schneeberger et al., 2013; Muylaert
et al., 2021), themselves likely to be driven by spatial effects,
especially at the local scale -- bats, indeed, occupy a variety of
environments, and therefore display a variety of adaptations to these
environments.

\begin{figure}
\hypertarget{fig:biogeo}{%
\centering
\includegraphics{figures/combined_biogeo.png}
\caption{Phylogeographic regions of bats (top) and viruses (bottom)
based on the joint analysis of their occurrence and phylogenetic
relatedness. The different colors show tendencies to separate alongside
the first two components of a PCoA. Note that the PCoA for the bats and
viruses are independent, and so cannot be compared directly -- that
being said, the regions can be compared across maps.}\label{fig:biogeo}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{Trivariate additive mapping of the components of risk in the
red/green/blue, where high virus sharing is encoded in the blue channel,
host phylogenetic diversity in the green channel, and compositional
uniqueness in the red channel. A pixel that would maximize all measures
would be a pure white (specifically RGB(1.0, 1.0. 1.0)), and a pixel
with the lowest possible values would be pure black (specifically
RGB(0.0, 0.0, 0.0)). Therefore, lighter values (the sum of the three
channels gets closer to 3) indicate higher risk, and the color indicates
the proportional distribution of the factors making up the total
risk.}\label{fig:trivariate}
}
\end{figure}
